---
title: "Combined Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
library(cowplot)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
visualization_output <- "../visualization_results/combined"
snaq_input_dir <- "../snaq_summary"
findgraph_input_dir <- "../findgraph_summary"
source("../scripts/visual_utilities.R")

parse_params <- function(df, param_col) {
  df %>% mutate(
    dup_loss_rate = as.numeric(str_extract(
      .data[[param_col]], "(?<=DUP)[0-9]*\\.?[0-9]+(?:[eE][-+]?[0-9]+)?")),
    RV    = factor(str_extract(.data[[param_col]], "(?<=RV)[A-Z]+"),
                   levels = c("N", "G", "L")),
    SF    = as.numeric(str_extract(
      .data[[param_col]], "(?<=SF)[0-9]*\\.?[0-9]+")),
    N_ind = as.integer(str_extract(.data[[param_col]], "(?<=N_ind)[0-9]+")),
    n_ind = N_ind
  )
}

snaq_df <- read_csv("../results/SNaQ_summary.csv") %>%
  parse_params("parameter_setting")
findgraph_df <- read_csv("../results/findgraph_summary.csv") %>%
  parse_params("paramname_root") %>%
  mutate(
    pct_H0        = H0Accepted / total_replicates * 100,
    pct_H0_wr_3.7 = H0Accepted_WR_3.7 / total_replicates * 100
  )
```

# Combined Plot of minor Gamma SNaQ vs findgraph
Minor gamma values aggregated across all parameter settings (n_inds, ILS, rates)
with substitution rate variation color coding (gene, lineage, none).

```{r combined_snaq_findgraph_minor_gamma, fig.width=14, fig.height=6}
# p_minor_gamma <- plot_combined_snaq_findgraph_aggregated(
#   snaq_input_dir      = snaq_input_dir,
#   findgraph_input_dir = findgraph_input_dir,
#   output_dir          = visualization_output,
#   output_filename     = "combined_snaq_findgraph_aggregated",
#   max_y               = 500
# )
# print(p_minor_gamma)
```

# Combined Plot of minor Gamma SNaQ vs findgraph for each parameter setting
Minor gamma values faceted by parameter settings (n_inds, ILS, dup/loss rates)
with substitution rate variation color coding (gene, lineage, none).

```{r combined_snaq_findgraph_minor_gamma_by_tree_display, fig.width=14, fig.height=18}
source("../scripts/visual_utilities.R")
result <- plot_combined_snaq_findgraph_by_tree_display(
  snaq_input_dir      = snaq_input_dir,
  findgraph_input_dir = findgraph_input_dir,
  output_dir          = visualization_output,
  output_filename     = "combined_snaq_findgraph_by_tree_display",
  max_y               = 350,
  max_y_by_ratevar    = list(none = 250, 
  gene = 350, 
  lineage = 250)
)
print(result)
```

# Combined H=1 True Graph Recovery: SNaQ vs findgraphs

```{r combined_h1_recovery, fig.width=16, fig.height=9}
# SNaQ: find_true_net1 = % reps where H=1 finds true graph (across all graphs)
# findgraphs uses pct_true_tree_H1 (same metric)
p_h1_recovery <- plot_combined_true_graph_recovery_H1_only(
  snaq_df          = snaq_df,
  findgraph_df     = findgraph_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "pct_true_tree_H1",
  output_dir       = visualization_output,
  output_filename  =
    "combined_snaq_findgraph_h1_alltrees_for_findgraphs_recovery",
  y_range          = c(75, 105),
  plot_title       = "H=1 True Graph Recovery: SNaQ vs findgraphs"
)
print(p_h1_recovery)
```

```{r combined_h1_best_graph_recovery, fig.width=16, fig.height=9}
# Best-graph version: findgraphs uses count_H1_best_displays_true_tree
source("../scripts/visual_utilities.R")
p_h1_best <- plot_combined_true_graph_recovery_H1_only(
  snaq_df          = snaq_df,
  findgraph_df     = findgraph_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "count_H1_best_displays_true_tree",
  output_dir       = visualization_output,
  output_filename  = "combined_snaq_findgraph_h1_best_graph_recovery",
  y_range          = c(60, 102),
  plot_title       = NULL
)
print(p_h1_best)
```

# Combined Type I Error Rate (H>=1 Accepted): SNaQ vs findgraphs

```{r combined_h0_acceptance, fig.width=16, fig.height=9}
source("../scripts/visual_utilities.R")
p_h0_combined <- plot_combined_hypothesis_acceptance_H0(
  snaq_df               = snaq_df,
  findgraph_df          = findgraph_df,
  h0_col_snaq           = "pct_H0",
  h0_col_findgraph_wr30 = "pct_H0",
  h0_col_findgraph_wr37 = "pct_H0_wr_3.7",
  output_dir            = visualization_output,
  output_filename       = "combined_snaq_findgraph_type1_error",
  y_range               = c(-5, 105),
  plot_title            = NULL
)
print(p_h0_combined)
```

# Three-Panel Combined Figure (cowplot)

Top-left: findgraphs WR 95th percentile jitter.  
Top-right: H=1 best graph recovery (SNaQ vs findgraphs).  
Bottom: Type I error rate (SNaQ vs findgraphs with WR thresholds).

Requires p_wr_jitter, p_h1_best, p_h0_combined from the previous three chunks.

```{r combined_three_panel_figure, fig.width=18, fig.height=16}
source("../scripts/visual_utilities.R")

# --- Figure 1: True-tree WR 95th-percentile jitter 
# (findgraphs, facet label added) ---
p_wr_jitter <- plot_WR_percentiles_jitter_combined(
  input_dir  = findgraph_input_dir,
  wr_column  = "true_tree_wr",
  output_dir = visualization_output,
  output_filename = "findgraph_true_tree_WR_95-percentiles_jitter_combined",
  ymax = 9,
  facet_label = "find_graphs"
)

# --- Shared legend: rate variation + ILS/n, 
# each group in its own box ---
p_for_shared_legend <- p_h0_combined +
  guides(
    color = guide_legend(
      name         = "rate variation:",
      override.aes = list(size = 8, stroke = 1.6),
      nrow         = 3,
      theme        = theme(
        legend.background = element_rect(color = "black", 
        linewidth = 1.2, fill = "white"),
        legend.text       = element_text(size = 19, face = "bold"),
        legend.title      = element_text(size = 19, face = "bold")
      )
    ),
    shape = guide_legend(
      name         = "ILS & individuals / taxon (n)",
      override.aes = list(size  = 8, stroke = 1.6,
                          fill  = c("grey55", "white", 
                          "grey55", "white"),
                          color = "black"),
      nrow  = 2,
      theme = theme(
        legend.background = element_rect(color = "black", 
                          linewidth = 1.2, fill = "white"),
        legend.text       = element_text(size = 19, 
                            face = "bold"),
        legend.title      = element_text(size = 19, 
                            face = "bold")
      )
    )
  ) +
  theme(
    legend.position  = "bottom",
    legend.box       = "horizontal",
    legend.spacing.x = unit(1.5, "lines")
  )
combined_legend <- cowplot::get_legend(p_for_shared_legend)

# =============================================================================
# Uniform font sizes across all three panels
#   axis.text = 20,  axis.title = 22,  strip.text = 21
# =============================================================================

COMMON_THEME <- theme(
  axis.title.x     = element_blank(), # x-label shown only on Fig 3
  axis.text.x      = element_text(size = 20, angle = 45, 
                                  hjust = 1,
                                  color = "black", face = "bold"),
  axis.text.y      = element_text(size = 20, color = "black", 
                                  face = "bold"),
  strip.text       = element_text(size = 21, face = "bold"),
  strip.background = element_rect(fill = "grey90"),
  legend.position  = "none"
)

# --- Fig 1 (panel A) ---
# WR threshold labels added inline; linetype legend suppressed
last_x <- tail(levels(p_wr_jitter$data$dup_loss_rate_cat), 1)

p1_noleg <- p_wr_jitter +
  COMMON_THEME +
  guides(linetype = "none") +
  labs(x = NULL, y = "95th percentile of worst residuals", 
        title = NULL) +
  theme(
    axis.title.y = element_text(size = 22, face = "bold", 
    margin = margin(r = 10)),
    plot.margin  = unit(c(0.5, 0.5, 0.2, 0.5), "lines")
  )

# --- Fig 2 (panel B) ---
# y-axis on right; 2.5-line left margin creates:
#   (a) a visible gap between panel A and panel B
#   (b) space outside the panel for the B label
p2_noleg <- p_h1_best +
  COMMON_THEME +
  scale_y_continuous(limits = c(60, 102), expand = c(0, 0)) +
  labs(x = NULL, y = "prob. of displaying the true tree (%)", 
          title = NULL) +
  theme(
    axis.title.y = element_text(size = 22, 
              face = "bold", margin = margin(r = 10)),
    plot.margin  = unit(c(0.5, 0.5, 0.2, 2.5), "lines")
  )

# --- Fig 3 (panel C) ---
p3_noleg <- p_h0_combined +
  theme(
    legend.position = "none",
    axis.title.x    = element_text(size = 22, 
                      face = "bold", margin = margin(t = 10)),
    axis.title.y    = element_text(size = 22, 
                      face = "bold", margin = margin(r = 10)),
    axis.text.x     = element_text(size = 20, angle = 45, hjust = 1,
                                   color = "black", face = "bold"),
    axis.text.y     = element_text(size = 20, 
                                    color = "black", face = "bold"),
    strip.text      = element_text(size = 21, face = "bold"),
    plot.margin     = unit(c(0.2, 0.5, 0.5, 0.5), "lines")
  )

# --- Assemble ---
# B label placed at label_x = 0.018: 
# with 2.5-line left margin on p2,
# that fraction falls inside the margin (left of the panel), 
# outside the data area.
top_row <- plot_grid(
  p1_noleg, p2_noleg,
  ncol           = 2,
  rel_widths     = c(1.1, 2),
  align          = "v",
  axis           = "tb",
  labels         = c("A", "B"),
  label_x        = c(0.005, 0.003),
  label_y        = 0.98,
  label_size     = 26,
  label_fontface = "bold"
)

main_grid <- plot_grid(
  top_row, p3_noleg,
  nrow           = 2,
  labels         = c("", "C"),
  label_x        = 0.005,
  label_y        = 0.98,
  label_size     = 26,
  label_fontface = "bold"
)

# Full figure with shared legend at bottom
final_figure <- plot_grid(
  main_grid,
  combined_legend,
  nrow        = 2,
  rel_heights = c(1, 0.12)
)

# Save
dir.create(visualization_output, showWarnings = FALSE, recursive = TRUE)
ggsave(
  file.path(visualization_output, "combined_three_panel_figure.pdf"),
  final_figure,
  width = 14, height = 14, dpi = 300, units = "in",
  device = cairo_pdf
)
print(final_figure)
```

# Three-Panel True Graph Recovery: findgraphs (best) / findgraphs (all) / SNaQ

```{r combined_true_graph_recovery_three_panel, fig.width=14, fig.height=20}
source("../scripts/visual_utilities.R")

# --- Panel A: findgraphs best-scoring graph ---
parts_A <- plot_true_graph_recovery_lines_aggregated(
  findgraph_df,
  h0_col     = "count_H0_best_is_true_tree",
  h1_col     = "count_H1_best_displays_true_tree",
  h1_noF_col = "count_H1_best_displays_true_tree_noF",
  output_dir      = visualization_output,
  output_filename = "findgraph_best_recovery_parts",
  y_range         = c(70, 102),
  return_parts    = TRUE
)


# --- Panel B: findgraphs all retained graphs ---
parts_B <- plot_true_graph_recovery_lines_aggregated(
  findgraph_df,
  h0_col     = "pct_true_tree_H0",
  h1_col     = "pct_true_tree_H1",
  h1_noF_col = "pct_true_tree_H1_noF",
  output_dir      = visualization_output,
  output_filename = "findgraph_all_recovery_parts",
  y_range         = c(90, 101),
  return_parts    = TRUE
)

# --- Panel C: SNaQ ---
parts_C <- plot_true_graph_recovery_lines_aggregated(
  snaq_df,
  output_dir      = visualization_output,
  output_filename = "snaq_recovery_parts",
  y_range         = c(65, 103),
  return_parts    = TRUE
)

# --- Strip panels: no legend; A/B lose x-axis; all titles top-left ---
PANEL_COMMON <- theme(
  legend.position = "none",
  plot.title      = element_text(hjust = 0, size = 19, face = "bold"),
  axis.title.y    = element_text(size = 22, face = "bold",
                                 margin = margin(r = 10)),
  axis.text.x     = element_text(size = 18, angle = 20, hjust = 1,
                                 color = "black", face = "bold"),
  axis.text.y     = element_text(size = 22, color = "black", face = "bold"),
  strip.text      = element_text(size = 22, face = "bold"),
  plot.margin     = unit(c(0.4, 0.5, 0.2, 0.5), "lines")
)

pA <- parts_A$p_no_legend +
  PANEL_COMMON +
  labs(title = "find_graphs: among best-scoring graphs") +
  theme(axis.title.x = element_blank())

pB <- parts_B$p_no_legend +
  PANEL_COMMON +
  labs(title = "find_graphs: among all retained graphs") +
  scale_y_continuous(limits = c(90, 101), expand = c(0, 0),
                     breaks = scales::breaks_pretty()) +
  theme(axis.title.x = element_blank())

pC <- parts_C$p_no_legend +
  PANEL_COMMON +
  labs(title = "SNaQ") +
  theme(
    plot.margin  = unit(c(0.2, 0.5, 0.4, 0.5), "lines"),
    axis.title.x = element_text(size = 22, face = "bold",
                                 margin = margin(t = 10))
  )

# --- Shared legend: rate variation (color) + ILS/n (shape), bottom box ---
legend_fill_override <- c("grey55", "white", "grey55", "white")

shared_legend_src <- parts_C$base_plot +
  theme(
    legend.position    = "bottom",
    legend.box         = "horizontal",
    legend.spacing.x   = unit(1.5, "lines"),
    legend.box.spacing = unit(0.0, "lines"),
    legend.margin      = margin(10, 10, 10, 10),
    legend.key.width   = unit(2.0, "cm"),
    legend.background  = element_rect(color = "black",
                                      linewidth = 1.2, fill = "white"),
    legend.text        = element_text(size = 18, face = "bold"),
    legend.title       = element_text(size = 18, face = "bold",
                                      hjust = 0, margin = margin(b = 4)),
    legend.title.position = "top"
  ) +
  guides(
    color = guide_legend(
      order        = 1,
      override.aes = list(size = 6, stroke = 1.4),
      ncol = 1
    ),
    shape = guide_legend(
      order        = 2,
      override.aes = list(
        size   = 6,
        stroke = 1.4,
        fill   = legend_fill_override,
        color  = "black"
      ),
      nrow = 2
    )
  )
shared_legend <- cowplot::get_legend(shared_legend_src)

# --- Assemble ---
panels <- plot_grid(
  pA, pB, pC,
  ncol           = 1,
  rel_heights    = c(1, 1, 1.15),
  labels         = c("A", "B", "C"),
  label_size     = 28,
  label_fontface = "bold",
  label_x        = 0.005,
  label_y        = 0.995
)

final_recovery <- plot_grid(
  panels,
  shared_legend,
  ncol        = 1,
  rel_heights = c(1, 0.12)
)

dir.create(visualization_output, showWarnings = FALSE, recursive = TRUE)
ggsave(
  file.path(visualization_output,
            "combined_true_graph_recovery_three_panel.pdf"),
  final_recovery,
  width = 12, height = 20, dpi = 300, units = "in"
)
print(final_recovery)
```

