
```{r}
---
title: "Simulation Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
```

## Load and Parse Data

```{r load-csv}
df <- read_csv("results/summary_concatenated.csv") 
outdir <- "visualization_results/simulation"
if (!dir.exists(outdir)) {
  dir.create(outdir, recursive = TRUE)
} 
```

```{r parse-data}
# Parse parameter_setting column
df <- df %>%
  mutate(
    dup_loss_rate = as.numeric(str_extract(parameter_setting, "(?<=DUP)[0-9.e+-]+(?=-)")),
    RV = str_extract(parameter_setting, "(?<=RV)[A-Z]+"),
    N_inds = as.integer(str_extract(parameter_setting, "(?<=N_ind)[0-9]+")),
    SF = as.numeric(str_extract(parameter_setting, "(?<=SF)[0-9.]+(?=(-|$))")),
    genelen = as.integer(str_extract(parameter_setting, "(?<=genelen)[0-9]+"))
  )

# Display parsed columns and check unique values
df %>% 
  select(parameter_setting, dup_loss_rate, RV, N_inds, SF, genelen) %>%
  head(10)

# Check unique values for each parameter
cat("Unique dup_loss_rate:", unique(df$dup_loss_rate), "\n")
cat("Unique SF:", unique(df$SF), "\n")
cat("Unique RV:", unique(df$RV), "\n")
cat("Unique N_inds:", unique(df$N_inds), "\n")
```

## Gene Events and Hidden Paralogy
This cell below plots 

```{r plot_events}
# Prepare data for plotting
plot_data <- df %>%
  select(dup_loss_rate, SF, RV, N_inds,
         pert_false_HP, pert_weak_HP, pert_strong_HP) %>%
  pivot_longer(cols = starts_with("pert_"), 
               names_to = "metric", 
               values_to = "percentage") %>%
  mutate(
    dup_loss_rate = factor(dup_loss_rate),
    SF = factor(SF),
    RV = factor(RV),
    N_inds = factor(N_inds),
    metric = factor(metric, levels = c(
      "pert_false_HP", "pert_weak_HP", "pert_strong_HP"
    )),
    metric_label = recode(metric,
      "pert_false_HP" = "false HP",
      "pert_weak_HP" = "weak HP",
      "pert_strong_HP" = "strong HP"
    ),
    # Create ILS label
    ILS_label = recode(SF,
      "0.5" = "low ILS",
      "1" = "high ILS"
    ),
    # Create individual per taxon label
    N_inds_label = paste(N_inds, "individual per taxon"),
    # Create combined shape factor (4 levels: 2 N_inds × 2 SF)
    shape_group = interaction(N_inds_label, ILS_label, sep = ", "),
    # Recode RV labels with specific order for color assignment
    RV_label = factor(recode(RV,
      "G" = "gene",
      "L" = "lineage",
      "N" = "none"
    ), levels = c("gene", "lineage", "none"))
  )

# Create combined plot with facet_grid
p_combined <- ggplot(plot_data, aes(x = dup_loss_rate, y = percentage, 
                                     color = RV_label, shape = shape_group)) +
  geom_point(size = 4, alpha = 0.7, position = position_jitter(width = 0.2, height = 0)) +
  facet_grid(~ metric_label, scales = "fixed") +
  scale_color_manual(values = c("gene" = "#619CFF", 
                                 "lineage" = "salmon", 
                                 "none" = "#00BA38")) +
  labs(title = "hidden paralogy across simulation conditions",
       x = "dup/loss rate",
       y = "percentage",
       color = "substitution rate variation",
       shape = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.box = "vertical")

ggsave(file.path(outdir, "percentage_events_plot_combined.pdf"), plot = p_combined, width = 10, height = 5, units = "in")
print(p_combined)

```

## Summary Statistics: Hidden Paralogy by Duplication/Loss Rate
It seems that SF and RateVar will not change HP statistics, so we summarize HP stats by N_inds and dup_loss_rate. (N_inds will not change ratevar as well). 
```{r summary-hp}
summary_df <- df %>%
  group_by(dup_loss_rate) %>%
  summarise(
    n_genes_mean = round(mean(n_genes, na.rm = TRUE),1),
    n_iterations = round(mean(n_iterations, na.rm = TRUE),1), 
    False_HP_mean = round(mean(pert_false_HP, na.rm = TRUE),1),
    False_HP_sd = round(sd(pert_false_HP, na.rm = TRUE),2),
    Weak_HP_mean = round(mean(pert_weak_HP, na.rm = TRUE),1),
    Weak_HP_sd = round(sd(pert_weak_HP, na.rm = TRUE),2),
    Strong_HP_mean = round(mean(pert_strong_HP, na.rm = TRUE),1),
    Strong_HP_sd = round(sd(pert_strong_HP, na.rm = TRUE),2),
    pert_gene_tree_noDupLoss_mean = round(mean(pert_trees_experiencing_nothing, na.rm = TRUE),1),
    pert_gene_tree_noDupLoss_sd = round(sd(pert_trees_experiencing_nothing, na.rm = TRUE),2),
    .groups = "drop", 
  ) %>%
  arrange(dup_loss_rate)
print(summary_df, width = Inf)
```

