---
title: "FindGraphs Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
library(latex2exp)
visual_output <- "visualization_results/findgraph" 
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) 
source("../scripts/visual_utilities.R")
```

## Load and Parse Data
```{r load-parse}
df <- read_csv("../results/findgraph_summary.csv") %>%
  mutate(
    dup_loss_rate = as.numeric(str_extract(paramname_root, 
      "(?<=DUP)[0-9]*\\.?[0-9]+(?:[eE][-+]?[0-9]+)?")),
    RV = factor(str_extract(paramname_root, "(?<=RV)[A-Z]+"),
                levels = c("N", "G", "L", "GL")),
    genelen = as.integer(str_extract(paramname_root, "(?<=genelen)[0-9]+")),
    SF = as.numeric(str_extract(paramname_root, "(?<=SF)[0-9]*\\.?[0-9]+")),
    N_ind = as.integer(str_extract(paramname_root, "(?<=N_ind)[0-9]+")),
    n_ind = N_ind,
    pct_H0 = H0Accepted / total_replicates * 100,
    pct_H1 = H1Accepted / total_replicates * 100,
    pct_BT1 = BT1Accepted / total_replicates * 100,
    pct_H0_wr_3.7 = H0Accepted_WR_3.7 / total_replicates * 100, 
    pct_H1_wr_3.7 = H1Accepted_WR_3.7 / total_replicates * 100,
    pct_BT1_wr_3.7 = BT1Accepted_WR_3.7 / total_replicates * 100 
  )
head(df)
```

## model choice by Rate Variation and Duplication/Loss Rate
```{r plot-hypothesis-acceptance-grid}
#| fig-width: 14
#| fig-height: 16
source("../scripts/visual_utilities.R")
library(cowplot)
# For findgraphs data
p <- plot_hypothesis_acceptance_grid(df, 
  value_col_prefix = "pct_",
  h_greater_col = "pct_BT1",
  output_dir = "../visualization_results/findgraph",
  plot_title = TeX("find_graphs model choice when WR $\\leq$ 3.0"),
  output_filename = "findgraphs_model_choice_WR3.0.png"
  ) + theme(legend.position = "none", axis.title.x = element_blank())

P_WR_3.7 <- plot_hypothesis_acceptance_grid(df, 
  h0_col = "pct_H0_wr_3.7",
  h1_col = "pct_H1_wr_3.7",
  h_greater_col = "pct_BT1_wr_3.7",
  output_dir = "../visualization_results/findgraph",
  plot_title = TeX("find_graphs model choice when WR $\\leq$ 3.7"),
  output_filename = "findgraphs_model_choice_WR_3.7.png")

combined <- plot_grid(p, P_WR_3.7, ncol = 1, 
        labels = c("A", "B"), label_size = 18)

png(filename = 
  "../visualization_results/findgraph/findgraphs_model_choice_combined.png", 
  width = 14, height = 16, units = "in", res = 300)
print(combined) 
dev.off() 

```


```{r plot-hypothesis-acceptance-H0-by-rate-variation}
#| fig-width: 12
#| fig-height: 6

# # Plot H=0 (tree) acceptance percentage by rate variation
# p_h0 <- plot_hypothesis_acceptance_H0_by_rate_variation(
#   df,
#   h0_col = "pct_H0",
#   output_dir = "../visualization_results/findgraph",
#   output_filename = "findgraphs_typeI_WR_3.0",
#   # plot_title = "findgraphs type I error rate under WR threshold = 3.0"
#   plot_title = NULL
#   )

# p_h0_wr3.7 <- plot_hypothesis_acceptance_H0_by_rate_variation(
#   df,
#   h0_col = "pct_H0_wr_3.7",
#   output_dir = "../visualization_results/findgraph",
#   output_filename = "findgraphs_typeI_WR_3.7",
#   plot_title = "findgraphs type I error rate under WR threshold = 3.7")

# # Display the plot
# print(p_h0)
# print(p_h0_wr3.7)
``` 


## True Graph Recovery by Duplication/Loss Rate
# plot recovery of the true tree based on all graphs found per replicate


# % reps recovering true tree (H=0/H=1, best graph, with/without F):
```{r}
# source("../scripts/visual_utilities.R")
# p_recovery_aggregated <- plot_true_graph_recovery_lines_aggregated(df, 
#   h0_col = "count_H0_best_is_true_tree",
#   h1_col = "count_H1_best_displays_true_tree",
#   h1_noF_col = "count_H1_best_displays_true_tree_noF",
#   output_dir = "../visualization_results/findgraph",
#   y_range = c(70, 102), 
#   # plot_title = "probability of displaying the true topology by find_graphs",
#   plot_title = NULL,
#   output_filename = "findgraph_best_graph_true_tree_recovery_aggregated.png"
# )
# print(p_recovery_aggregated)
```

# Plot graph recovery for H=1 only
```{r}
#| fig-width: 12
#| fig-height: 6

# Plot H=1 only recovery rates (% finding true tree)
# # p_h1_only_pct <- plot_true_graph_recovery_H1_only(df,
# #   h1_col = "pct_true_tree_H1",  # % of all graphs recovering the true tree
# #   output_dir = "../visualization_results/findgraph",
# #   output_filename = "true_graph_recovery_H1_only_all_graphs.pdf")

# # print(p_h1_only_pct)
```

```{r}
#| fig-width: 12
#| fig-height: 6

# Plot H=1 only recovery rates (best graph counts)
# p_h1_only_count <- plot_true_graph_recovery_H1_only(df,
#   h1_col = "count_H1_best_displays_true_tree",  # best graphs displaying true
#   output_dir = "../visualization_results/findgraph",
#   plot_title = "findgraphs true graph recovery under H=1 (top tree only)", 
#   y_range = c(70, 102), 
#   output_filename = "findgraph_true_graph_recovery_H1_only_best_graph.pdf")
# print(p_h1_only_count)
```

```{r plot-true-graph-recovery}
#| fig-width: 16
#| fig-height: 8

# Plot true graph recovery across all parameter combinations
# p2 <- plot_true_graph_recovery_lines(df,
#   h0_col = "pct_true_tree_H0",
#   h1_col = "pct_true_tree_H1",
#   h1_noF_col = "pct_true_tree_H1_noF",
#   output_dir = "../visualization_results/findgraphs",
#   output_filename = "true_graph_recovery_lines.pdf"
# )

# # Display the plot
# print(p2)
```

```{r}
# Plot true graph recovery across all parameter combinations
# p3 <- plot_true_graph_recovery_lines(df,
#   h0_col = "count_H0_best_is_true_tree",
#   h1_col = "count_H1_best_displays_true_tree",
#   h1_noF_col = "count_H1_best_displays_true_tree_noF",
#   output_dir = "../visualization_results/findgraph",
#   output_filename = "true_graph_best_graph_recovery_lines.pdf"
# )
# print(p3)
```

## Taxon Recovery Heatmap (LEGACY — disabled)

> **LEGACY (disabled for Dryad/paper submission, 2026-05).** The taxon-recovery
> heatmap is not in the published paper. The upstream input
> (`results/findgraph_taxon_recovery.csv`) is no longer produced by
> `scripts/summary_findgraph.jl`, and `plot_taxon_recovery_heatmaps()` in
> `scripts/visual_utilities.R` is gated by a `stop()`. To re-enable:
> (1) uncomment the taxon-recovery block in `scripts/summary_findgraph.jl`,
> (2) remove the `stop()` in `plot_taxon_recovery_heatmaps()`,
> (3) uncomment the call below and re-render.

```{r plot-taxon-recovery-heatmaps}
#| fig-width: 15
#| fig-height: 12

# Plot taxon recovery rates by role and parameter setting
# plot_taxon_recovery_heatmaps(
#   input_long = "../results/findgraph_taxon_recovery.csv",
#   input_dir = "../results",
#   output_dir = "../visualization_results/findgraph",
#   colormap = "Blues"
# )
```
