---
title: "Combined Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
library(cowplot)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
visualization_output <- "../visualization_results/combined"
snaq_input_dir <- "../snaq_summary"
findgraph_input_dir <- "../findgraph_summary"
source("../scripts/visual_utilities.R")

parse_params <- function(df, param_col) {
  df %>% mutate(
    dup_loss_rate = as.numeric(str_extract(
      .data[[param_col]], "(?<=DUP)[0-9]*\\.?[0-9]+(?:[eE][-+]?[0-9]+)?")),
    RV    = factor(str_extract(.data[[param_col]], "(?<=RV)[A-Z]+"),
                   levels = c("N", "G", "L")),
    SF    = as.numeric(str_extract(
      .data[[param_col]], "(?<=SF)[0-9]*\\.?[0-9]+")),
    N_ind = as.integer(str_extract(.data[[param_col]], "(?<=N_ind)[0-9]+")),
    n_ind = N_ind
  )
}

snaq_df <- read_csv("../results/SNaQ_summary.csv") %>%
  parse_params("parameter_setting")
findgraph_df <- read_csv("../results/findgraph_summary.csv") %>%
  parse_params("paramname_root") %>%
  mutate(
    pct_H0        = H0Accepted / total_replicates * 100,
    pct_H0_wr_3.7 = H0Accepted_WR_3.7 / total_replicates * 100
  )

# PhyNEST (optional): produced by scripts/summary_phynest.jl.
# pct_H0 uses the calibrated threshold T* on the per-site T (score
# difference divided by the number of sites of the replicate's alignment),
# pct_H0_naive uses the sign of the score difference (T > 0).
phynest_input_dir <- "../phynest_summary"
phynest_file      <- "../results/PhyNEST_summary.csv"
phynest_df <- NULL
if (file.exists(phynest_file)) {
  phynest_df <- read_csv(phynest_file) %>%
    parse_params("parameter_setting") %>%
    mutate(
      pct_H0       = `H=0Accepted` / n_reps * 100,
      pct_H0_naive = `H=0Accepted_naive` / n_reps * 100
    )
  thresholds <- read_csv("../results/PhyNEST_T_threshold.csv")
  t_star <- c(low  = thresholds$T_star[thresholds$cell == "SF0.5-N_ind1"],
              high = thresholds$T_star[thresholds$cell == "SF1.0-N_ind1"])
}
```

# Combined Plot of minor Gamma SNaQ vs findgraph
Minor gamma values aggregated across all parameter settings (n_inds, ILS, rates)
with substitution rate variation color coding (gene, lineage, none).

```{r combined_snaq_findgraph_minor_gamma, fig.width=14, fig.height=6}
# p_minor_gamma <- plot_combined_snaq_findgraph_aggregated(
#   snaq_input_dir      = snaq_input_dir,
#   findgraph_input_dir = findgraph_input_dir,
#   output_dir          = visualization_output,
#   output_filename     = "combined_snaq_findgraph_aggregated",
#   max_y               = 500
# )
# print(p_minor_gamma)
```

# Combined Plot of minor Gamma SNaQ vs findgraph for each parameter setting
Minor gamma values faceted by parameter settings (n_inds, ILS, dup/loss rates)
with substitution rate variation color coding (gene, lineage, none).

```{r combined_snaq_findgraph_minor_gamma_by_tree_display, fig.width=14, fig.height=18}
source("../scripts/visual_utilities.R")
result <- plot_combined_snaq_findgraph_by_tree_display(
  snaq_input_dir      = snaq_input_dir,
  findgraph_input_dir = findgraph_input_dir,
  output_dir          = visualization_output,
  output_filename     = "combined_snaq_findgraph_by_tree_display",
  max_y               = 350,
  max_y_by_ratevar    = list(none = 250, 
  gene = 350, 
  lineage = 250)
)
print(result)
```

# Combined H=1 True Graph Recovery: SNaQ vs findgraphs

```{r combined_h1_recovery, fig.width=16, fig.height=9}
# SNaQ: find_true_net1 = % reps where H=1 finds true graph (across all graphs)
# findgraphs uses pct_true_tree_H1 (same metric)
p_h1_recovery <- plot_combined_true_graph_recovery_H1_only(
  snaq_df          = snaq_df,
  findgraph_df     = findgraph_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "pct_true_tree_H1",
  output_dir       = visualization_output,
  output_filename  =
    "combined_snaq_findgraph_h1_alltrees_for_findgraphs_recovery",
  y_range          = c(75, 105),
  plot_title       = "H=1 True Graph Recovery: SNaQ vs findgraphs"
)
print(p_h1_recovery)
```

```{r combined_h1_best_graph_recovery, fig.width=16, fig.height=9}
# Best-graph version: findgraphs uses count_H1_best_displays_true_tree
source("../scripts/visual_utilities.R")
p_h1_best <- plot_combined_true_graph_recovery_H1_only(
  snaq_df          = snaq_df,
  findgraph_df     = findgraph_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "count_H1_best_displays_true_tree",
  output_dir       = visualization_output,
  output_filename  = "combined_snaq_findgraph_h1_best_graph_recovery",
  y_range          = c(60, 102),
  plot_title       = NULL
)
print(p_h1_best)
```

# Combined Type I Error Rate (H>=1 Accepted): SNaQ vs findgraphs

```{r combined_h0_acceptance, fig.width=16, fig.height=9}
source("../scripts/visual_utilities.R")
p_h0_combined <- plot_combined_hypothesis_acceptance_H0(
  snaq_df               = snaq_df,
  findgraph_df          = findgraph_df,
  h0_col_snaq           = "pct_H0",
  h0_col_findgraph_wr30 = "pct_H0",
  h0_col_findgraph_wr37 = "pct_H0_wr_3.7",
  output_dir            = visualization_output,
  output_filename       = "combined_snaq_findgraph_type1_error",
  y_range               = c(-5, 105),
  plot_title            = NULL
)
print(p_h0_combined)
```

# Three-Panel Combined Figure (cowplot)

Top-left: findgraphs WR 95th percentile jitter.  
Top-right: H=1 best graph recovery (SNaQ vs findgraphs).  
Bottom: Type I error rate (SNaQ vs findgraphs with WR thresholds).

Requires p_wr_jitter, p_h1_best, p_h0_combined from the previous three chunks.

```{r combined_three_panel_figure, fig.width=18, fig.height=16}
source("../scripts/visual_utilities.R")

# --- Figure 1: True-tree WR 95th-percentile jitter 
# (findgraphs, facet label added) ---
p_wr_jitter <- plot_WR_percentiles_jitter_combined(
  input_dir  = findgraph_input_dir,
  wr_column  = "true_tree_wr",
  output_dir = visualization_output,
  output_filename = "findgraph_true_tree_WR_95-percentiles_jitter_combined",
  ymax = 9,
  facet_label = "find_graphs"
)

# --- Shared legend: rate variation + ILS/n, 
# each group in its own box ---
p_for_shared_legend <- p_h0_combined +
  guides(
    color = guide_legend(
      name         = "rate variation:",
      override.aes = list(size = 8, stroke = 1.6),
      nrow         = 3,
      theme        = theme(
        legend.background = element_rect(color = "black", 
        linewidth = 1.2, fill = "white"),
        legend.text       = element_text(size = 19, face = "bold"),
        legend.title      = element_text(size = 19, face = "bold")
      )
    ),
    shape = guide_legend(
      name         = "ILS & individuals / taxon (n)",
      override.aes = list(size  = 8, stroke = 1.6,
                          fill  = c("grey55", "white", 
                          "grey55", "white"),
                          color = "black"),
      nrow  = 2,
      theme = theme(
        legend.background = element_rect(color = "black", 
                          linewidth = 1.2, fill = "white"),
        legend.text       = element_text(size = 19, 
                            face = "bold"),
        legend.title      = element_text(size = 19, 
                            face = "bold")
      )
    )
  ) +
  theme(
    legend.position  = "bottom",
    legend.box       = "horizontal",
    legend.spacing.x = unit(1.5, "lines")
  )
combined_legend <- cowplot::get_legend(p_for_shared_legend)

# =============================================================================
# Uniform font sizes across all three panels
#   axis.text = 20,  axis.title = 22,  strip.text = 21
# =============================================================================

COMMON_THEME <- theme(
  axis.title.x     = element_blank(), # x-label shown only on Fig 3
  axis.text.x      = element_text(size = 20, angle = 45, 
                                  hjust = 1,
                                  color = "black", face = "bold"),
  axis.text.y      = element_text(size = 20, color = "black", 
                                  face = "bold"),
  strip.text       = element_text(size = 21, face = "bold"),
  strip.background = element_rect(fill = "grey90"),
  legend.position  = "none"
)

# --- Fig 1 (panel A) ---
# WR threshold labels added inline; linetype legend suppressed
last_x <- tail(levels(p_wr_jitter$data$dup_loss_rate_cat), 1)

p1_noleg <- p_wr_jitter +
  COMMON_THEME +
  guides(linetype = "none") +
  labs(x = NULL, y = "95th percentile of worst residuals", 
        title = NULL) +
  theme(
    axis.title.y = element_text(size = 22, face = "bold", 
    margin = margin(r = 10)),
    plot.margin  = unit(c(0.5, 0.5, 0.2, 0.5), "lines")
  )

# --- Fig 2 (panel B) ---
# y-axis on right; 2.5-line left margin creates:
#   (a) a visible gap between panel A and panel B
#   (b) space outside the panel for the B label
p2_noleg <- p_h1_best +
  COMMON_THEME +
  scale_y_continuous(limits = c(60, 102), expand = c(0, 0)) +
  labs(x = NULL, y = "prob. of displaying the true tree (%)", 
          title = NULL) +
  theme(
    axis.title.y = element_text(size = 22, 
              face = "bold", margin = margin(r = 10)),
    plot.margin  = unit(c(0.5, 0.5, 0.2, 2.5), "lines")
  )

# --- Fig 3 (panel C) ---
p3_noleg <- p_h0_combined +
  theme(
    legend.position = "none",
    axis.title.x    = element_text(size = 22, 
                      face = "bold", margin = margin(t = 10)),
    axis.title.y    = element_text(size = 22, 
                      face = "bold", margin = margin(r = 10)),
    axis.text.x     = element_text(size = 20, angle = 45, hjust = 1,
                                   color = "black", face = "bold"),
    axis.text.y     = element_text(size = 20, 
                                    color = "black", face = "bold"),
    strip.text      = element_text(size = 21, face = "bold"),
    plot.margin     = unit(c(0.2, 0.5, 0.5, 0.5), "lines")
  )

# --- Assemble ---
# B label placed at label_x = 0.018: 
# with 2.5-line left margin on p2,
# that fraction falls inside the margin (left of the panel), 
# outside the data area.
top_row <- plot_grid(
  p1_noleg, p2_noleg,
  ncol           = 2,
  rel_widths     = c(1.1, 2),
  align          = "v",
  axis           = "tb",
  labels         = c("A", "B"),
  label_x        = c(0.005, 0.003),
  label_y        = 0.98,
  label_size     = 26,
  label_fontface = "bold"
)

main_grid <- plot_grid(
  top_row, p3_noleg,
  nrow           = 2,
  labels         = c("", "C"),
  label_x        = 0.005,
  label_y        = 0.98,
  label_size     = 26,
  label_fontface = "bold"
)

# Full figure with shared legend at bottom
final_figure <- plot_grid(
  main_grid,
  combined_legend,
  nrow        = 2,
  rel_heights = c(1, 0.12)
)

# Save
dir.create(visualization_output, showWarnings = FALSE, recursive = TRUE)
ggsave(
  file.path(visualization_output, "combined_three_panel_figure.pdf"),
  final_figure,
  width = 14, height = 14, dpi = 300, units = "in",
  device = cairo_pdf
)
print(final_figure)
```

# Three-Panel True Graph Recovery: findgraphs (best) / findgraphs (all) / SNaQ

```{r combined_true_graph_recovery_three_panel, fig.width=14, fig.height=20}
source("../scripts/visual_utilities.R")

# --- Panel A: findgraphs best-scoring graph ---
parts_A <- plot_true_graph_recovery_lines_aggregated(
  findgraph_df,
  h0_col     = "count_H0_best_is_true_tree",
  h1_col     = "count_H1_best_displays_true_tree",
  h1_noF_col = "count_H1_best_displays_true_tree_noF",
  output_dir      = visualization_output,
  output_filename = "findgraph_best_recovery_parts",
  y_range         = c(70, 102),
  return_parts    = TRUE
)


# --- Panel B: findgraphs all retained graphs ---
parts_B <- plot_true_graph_recovery_lines_aggregated(
  findgraph_df,
  h0_col     = "pct_true_tree_H0",
  h1_col     = "pct_true_tree_H1",
  h1_noF_col = "pct_true_tree_H1_noF",
  output_dir      = visualization_output,
  output_filename = "findgraph_all_recovery_parts",
  y_range         = c(90, 101),
  return_parts    = TRUE
)

# --- Panel C: SNaQ ---
parts_C <- plot_true_graph_recovery_lines_aggregated(
  snaq_df,
  output_dir      = visualization_output,
  output_filename = "snaq_recovery_parts",
  y_range         = c(65, 103),
  return_parts    = TRUE
)

# --- Strip panels: no legend; A/B lose x-axis; all titles top-left ---
PANEL_COMMON <- theme(
  legend.position = "none",
  plot.title      = element_text(hjust = 0, size = 19, face = "bold"),
  axis.title.y    = element_text(size = 22, face = "bold",
                                 margin = margin(r = 10)),
  axis.text.x     = element_text(size = 18, angle = 20, hjust = 1,
                                 color = "black", face = "bold"),
  axis.text.y     = element_text(size = 22, color = "black", face = "bold"),
  strip.text      = element_text(size = 22, face = "bold"),
  plot.margin     = unit(c(0.4, 0.5, 0.2, 0.5), "lines")
)

pA <- parts_A$p_no_legend +
  PANEL_COMMON +
  labs(title = "find_graphs: among best-scoring graphs") +
  theme(axis.title.x = element_blank())

pB <- parts_B$p_no_legend +
  PANEL_COMMON +
  labs(title = "find_graphs: among all retained graphs") +
  scale_y_continuous(limits = c(90, 101), expand = c(0, 0),
                     breaks = scales::breaks_pretty()) +
  theme(axis.title.x = element_blank())

pC <- parts_C$p_no_legend +
  PANEL_COMMON +
  labs(title = "SNaQ") +
  theme(
    plot.margin  = unit(c(0.2, 0.5, 0.4, 0.5), "lines"),
    axis.title.x = element_text(size = 22, face = "bold",
                                 margin = margin(t = 10))
  )

# --- Shared legend: rate variation (color) + ILS/n (shape), bottom box ---
legend_fill_override <- c("grey55", "white", "grey55", "white")

shared_legend_src <- parts_C$base_plot +
  theme(
    legend.position    = "bottom",
    legend.box         = "horizontal",
    legend.spacing.x   = unit(1.5, "lines"),
    legend.box.spacing = unit(0.0, "lines"),
    legend.margin      = margin(10, 10, 10, 10),
    legend.key.width   = unit(2.0, "cm"),
    legend.background  = element_rect(color = "black",
                                      linewidth = 1.2, fill = "white"),
    legend.text        = element_text(size = 18, face = "bold"),
    legend.title       = element_text(size = 18, face = "bold",
                                      hjust = 0, margin = margin(b = 4)),
    legend.title.position = "top"
  ) +
  guides(
    color = guide_legend(
      order        = 1,
      override.aes = list(size = 6, stroke = 1.4),
      ncol = 1
    ),
    shape = guide_legend(
      order        = 2,
      override.aes = list(
        size   = 6,
        stroke = 1.4,
        fill   = legend_fill_override,
        color  = "black"
      ),
      nrow = 2
    )
  )
shared_legend <- cowplot::get_legend(shared_legend_src)

# --- Assemble ---
panels <- plot_grid(
  pA, pB, pC,
  ncol           = 1,
  rel_heights    = c(1, 1, 1.15),
  labels         = c("A", "B", "C"),
  label_size     = 28,
  label_fontface = "bold",
  label_x        = 0.005,
  label_y        = 0.995
)

final_recovery <- plot_grid(
  panels,
  shared_legend,
  ncol        = 1,
  rel_heights = c(1, 0.12)
)

dir.create(visualization_output, showWarnings = FALSE, recursive = TRUE)
ggsave(
  file.path(visualization_output,
            "combined_true_graph_recovery_three_panel.pdf"),
  final_recovery,
  width = 12, height = 20, dpi = 300, units = "in"
)
print(final_recovery)
```



# Figures including PhyNEST

The chunks below add PhyNEST as a third method. They only run when
`results/PhyNEST_summary.csv` exists (see `scripts/summary_phynest.jl`); the
figures above are unchanged.

## H=1 true tree recovery: find_graphs (best graph) / SNaQ / PhyNEST

```{r phynest_h1_recovery, fig.width=18, fig.height=9, eval=!is.null(phynest_df)}
source("../scripts/visual_utilities.R")
p_h1_three <- plot_combined_true_graph_recovery_H1_only(
  snaq_df          = snaq_df,
  findgraph_df     = findgraph_df,
  phynest_df       = phynest_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "count_H1_best_displays_true_tree",
  h1_col_phynest   = "find_true_net1",
  output_dir       = visualization_output,
  output_filename  = "combined_three_methods_h1_best_graph_recovery",
  y_range          = c(0, 102),
  plot_title       = NULL
)
print(p_h1_three)
```

## Type I error: find_graphs (WR 3.0 / 3.7), SNaQ, PhyNEST (T > T*)

The naive PhyNEST rule (T > 0) is not shown here (it selects h=1 in every
replicate; see `PhyNEST_model_choice_combined.png`).

```{r phynest_type1_error, fig.width=20, fig.height=9, eval=!is.null(phynest_df)}
p_h0_three <- plot_combined_hypothesis_acceptance_H0(
  snaq_df               = snaq_df,
  findgraph_df          = findgraph_df,
  phynest_df            = phynest_df,
  h0_col_snaq           = "pct_H0",
  h0_col_findgraph_wr30 = "pct_H0",
  h0_col_findgraph_wr37 = "pct_H0_wr_3.7",
  h0_col_phynest_naive  = NULL,
  h0_col_phynest_tstar  = "pct_H0",
  output_dir            = visualization_output,
  output_filename       = "combined_three_methods_type1_error",
  y_range               = c(-5, 105),
  plot_title            = NULL
)
print(p_h0_three)
```

## Model choice: SNaQ (A) and PhyNEST with T > T* (B) in one figure

Supplementary figure replacing the separate SNaQ and PhyNEST model-choice
figures. The naive PhyNEST rule (T > 0) is not shown.

```{r combined_model_choice_snaq_phynest, fig.width=14, fig.height=18, eval=!is.null(phynest_df)}
snaq_mc <- snaq_df %>%
  mutate(pct_H0 = `H=0Accepted`, pct_H1 = `H=1Accepted`,
         pct_H_greater = `H>1Accepted`)
phynest_mc <- phynest_df %>%
  mutate(pct_H1 = `H=1Accepted` / n_reps * 100,
         pct_H_greater = `H>1Accepted` / n_reps * 100)
# each panel keeps its own legend: PhyNEST only fits h=0 and h=1, so a
# selected reticulation is h >= 1 for PhyNEST
p_mc_snaq <- plot_hypothesis_acceptance_grid(snaq_mc,
  output_dir = visualization_output,
  output_filename = "snaq_model_choice_part.png",
  plot_title = "SNaQ") +
  theme(axis.title.x = element_blank())
p_mc_phynest <- plot_hypothesis_acceptance_grid(phynest_mc,
  output_dir = visualization_output,
  output_filename = "phynest_model_choice_part.png",
  plot_title = "PhyNEST (T > T*)",
  h_labels = c("h=0 (tree)", "h\u22651 (network)", "h>1 (network)"),
  show_h_greater = FALSE)
mc_stack <- plot_grid(p_mc_snaq, p_mc_phynest, ncol = 1,
                      rel_heights = c(1.65, 1.15),
                      labels = c("A", "B"), label_size = 18)
png(filename = file.path(visualization_output,
                         "combined_model_choice_snaq_phynest.png"),
    width = 14, height = 18, units = "in", res = 300)
print(mc_stack)
dev.off()
print(mc_stack)
```

## Minor gamma by tree display: find_graphs / SNaQ / PhyNEST

```{r phynest_minor_gamma_by_tree_display, fig.width=16, fig.height=18, eval=!is.null(phynest_df)}
result_three <- plot_combined_snaq_findgraph_by_tree_display(
  snaq_input_dir      = snaq_input_dir,
  findgraph_input_dir = findgraph_input_dir,
  phynest_input_dir   = phynest_input_dir,
  output_dir          = visualization_output,
  output_filename     = "combined_three_methods_by_tree_display",
  max_y               = 350,
  max_y_by_ratevar    = list(none = 250, gene = 350, lineage = 250)
)
print(result_three)
```

## Per-replicate WR (find_graphs) and T (PhyNEST) with their thresholds

Supplementary figure: (A) worst residual of the true tree in every
find_graphs replicate, one panel per ILS level and number of individuals;
(B) T in every PhyNEST replicate (one individual per taxon), one panel per
ILS level, with T*.

```{r combined_WR_T_distributions_jitter, fig.width=12, fig.height=19, eval=!is.null(phynest_df)}
p_wr_points <- plot_WR_distributions_jitter(
  input_dir       = findgraph_input_dir,
  output_dir      = "../visualization_results/findgraph",
  output_filename = "findgraph_true_tree_WR_distributions_jitter"
)
p_T_points <- plot_T_distributions(
  input_dir       = phynest_input_dir,
  output_dir      = "../visualization_results/phynest",
  output_filename = "PhyNEST_T_distributions",
  t_star          = t_star
)
# the rate-variation legend is shown once, under the PhyNEST panel
wr_T_points <- plot_grid(
  p_wr_points + labs(title = "find_graphs") + guides(color = "none") +
    theme(plot.title = element_text(size = 22, face = "bold", hjust = 0.5)),
  p_T_points + labs(title = "PhyNEST") +
    theme(plot.title = element_text(size = 22, face = "bold", hjust = 0.5)),
  ncol = 1, rel_heights = c(11, 8), labels = c("A", "B"),
  label_size = 26, label_fontface = "bold")
ggsave(file.path(visualization_output,
                 "combined_WR_T_distributions_jitter.png"),
       wr_T_points, width = 12, height = 19, dpi = 300, units = "in",
       bg = "white")
print(wr_T_points)
```

## Four-panel main figure with PhyNEST

Top: (A) find_graphs WR 95th percentile, (B) PhyNEST T 95th percentile
with T*, (C) H=1 recovery for the three methods. Bottom: (D) type I error.
Same fonts as the three-panel figure above.

```{r combined_four_panel_figure_with_phynest, fig.width=20, fig.height=16, eval=!is.null(phynest_df)}
source("../scripts/visual_utilities.R")

p_wr_jitter <- plot_WR_percentiles_jitter_combined(
  input_dir       = findgraph_input_dir,
  wr_column       = "true_tree_wr",
  output_dir      = visualization_output,
  output_filename = "findgraph_true_tree_WR_95-percentiles_jitter_combined",
  ymax            = 9,
  facet_label     = "find_graphs"
)
p_T_jitter <- plot_T_percentiles_jitter(
  input_dir       = phynest_input_dir,
  output_dir      = visualization_output,
  output_filename = "PhyNEST_T_95-percentiles_jitter",
  t_star          = t_star,
  label_t_star    = FALSE,
  facet_label     = "PhyNEST"
)

combined_legend <- cowplot::get_legend(
  p_h0_three +
    guides(
      color = guide_legend(
        name = "rate variation:",
        override.aes = list(size = 8, stroke = 1.6), nrow = 3,
        theme = theme(
          legend.background = element_rect(color = "black",
                                           linewidth = 1.2, fill = "white"),
          legend.text  = element_text(size = 19, face = "bold"),
          legend.title = element_text(size = 19, face = "bold"))),
      shape = guide_legend(
        name = "ILS & individuals / taxon (n)",
        override.aes = list(size = 8, stroke = 1.6,
                            fill = c("grey55", "white", "grey55", "white"),
                            color = "black"), nrow = 2,
        theme = theme(
          legend.background = element_rect(color = "black",
                                           linewidth = 1.2, fill = "white"),
          legend.text  = element_text(size = 19, face = "bold"),
          legend.title = element_text(size = 19, face = "bold")))
    ) +
    theme(legend.position = "bottom", legend.box = "horizontal",
          legend.spacing.x = unit(1.5, "lines")))

COMMON_THEME <- theme(
  axis.title.x     = element_blank(),
  axis.text.x      = element_text(size = 20, angle = 45, hjust = 1,
                                  color = "black", face = "bold"),
  axis.text.y      = element_text(size = 20, color = "black", face = "bold"),
  strip.text       = element_text(size = 21, face = "bold"),
  strip.background = element_rect(fill = "grey90"),
  legend.position  = "none"
)

pA_main <- p_wr_jitter + COMMON_THEME + guides(linetype = "none") +
  labs(x = NULL, y = "95th percentile of worst residuals", title = NULL) +
  theme(axis.title.y = element_text(size = 22, face = "bold",
                                    margin = margin(r = 10)),
        plot.margin  = unit(c(0.5, 0.5, 0.2, 0.5), "lines"))

# panel B: the two T* lines (solid grey = low ILS, dashed black = high
# ILS) are described in the caption; the shared legend covers color/shape
pB_main <- p_T_jitter + COMMON_THEME +
  labs(x = NULL, y = "95th percentile of T", title = NULL) +
  theme(axis.title.y = element_text(size = 22, face = "bold",
                                    margin = margin(r = 10)),
        plot.margin  = unit(c(0.5, 0.5, 0.2, 1.5), "lines"))

pC_main <- p_h1_three + COMMON_THEME +
  scale_y_continuous(limits = c(0, 102), expand = c(0, 0)) +
  labs(x = NULL, y = "prob. of displaying the true tree (%)", title = NULL) +
  theme(axis.title.y = element_text(size = 22, face = "bold",
                                    margin = margin(r = 10)),
        plot.margin  = unit(c(0.5, 0.5, 0.2, 1.5), "lines"))

pD_main <- p_h0_three +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 22, face = "bold",
                                    margin = margin(t = 10)),
        axis.title.y = element_text(size = 22, face = "bold",
                                    margin = margin(r = 10)),
        axis.text.x  = element_text(size = 20, angle = 45, hjust = 1,
                                    color = "black", face = "bold"),
        axis.text.y  = element_text(size = 20, color = "black", face = "bold"),
        strip.text   = element_text(size = 21, face = "bold"),
        plot.margin  = unit(c(0.2, 0.5, 0.5, 0.5), "lines"))

top_row <- plot_grid(pA_main, pB_main, pC_main, ncol = 3,
                     rel_widths = c(1, 1.1, 2.4),
                     align = "h", axis = "tb",
                     labels = c("A", "B", "C"),
                     label_x = 0.005, label_y = 0.98,
                     label_size = 26, label_fontface = "bold")
main_grid <- plot_grid(top_row, pD_main, nrow = 2, labels = c("", "D"),
                       label_x = 0.005, label_y = 0.98,
                       label_size = 26, label_fontface = "bold")
final_figure <- plot_grid(main_grid, combined_legend, nrow = 2,
                          rel_heights = c(1, 0.12))

ggsave(file.path(visualization_output,
                 "combined_four_panel_figure_with_phynest.pdf"),
       final_figure, width = 20, height = 14, dpi = 300, units = "in",
       device = cairo_pdf)
print(final_figure)
```

## Four-panel true tree recovery: find_graphs (best) / find_graphs (all) / SNaQ / PhyNEST

Requires pA, pB, parts_C, PANEL_COMMON and shared_legend from the
three-panel recovery chunk above.

```{r combined_true_graph_recovery_four_panel, fig.width=14, fig.height=26, eval=!is.null(phynest_df)}
parts_D <- plot_true_graph_recovery_lines_aggregated(
  phynest_df,
  output_dir      = visualization_output,
  output_filename = "phynest_recovery_parts",
  y_range         = c(0, 103),
  return_parts    = TRUE
)
pD_rec <- parts_D$p_no_legend +
  PANEL_COMMON +
  labs(title = "PhyNEST") +
  theme(plot.margin  = unit(c(0.2, 0.5, 0.4, 0.5), "lines"),
        axis.title.x = element_text(size = 22, face = "bold",
                                    margin = margin(t = 10)))
# SNaQ is no longer the bottom panel, so it loses the x-axis title
pC_rec <- parts_C$p_no_legend + PANEL_COMMON +
  labs(title = "SNaQ") + theme(axis.title.x = element_blank())

panels4 <- plot_grid(pA, pB, pC_rec, pD_rec, ncol = 1,
                     rel_heights = c(1, 1, 1, 1.15),
                     labels = c("A", "B", "C", "D"), label_size = 28,
                     label_fontface = "bold", label_x = 0.005, label_y = 0.995)
final_recovery4 <- plot_grid(panels4, shared_legend, ncol = 1,
                             rel_heights = c(1, 0.1))
ggsave(file.path(visualization_output,
                 "combined_true_graph_recovery_four_panel.pdf"),
       final_recovery4, width = 12, height = 26, dpi = 300, units = "in")
print(final_recovery4)
```

## True tree recovery split in two figures: find_graphs / SNaQ + PhyNEST

Same panels as the four-panel figure, as two supplementary figures of two
panels each, both with the shared legend.

```{r combined_true_graph_recovery_split, fig.width=12, fig.height=14, eval=!is.null(phynest_df)}
X_TITLE <- theme(axis.title.x = element_text(size = 22, face = "bold",
                                             margin = margin(t = 10)),
                 plot.margin  = unit(c(0.2, 0.5, 0.4, 0.5), "lines"))
two_panels <- function(top, bottom, filename) {
  fig <- plot_grid(
    plot_grid(top, bottom, ncol = 1, rel_heights = c(1, 1.15),
              labels = c("A", "B"), label_size = 28, label_fontface = "bold",
              label_x = 0.005, label_y = 0.995),
    shared_legend, ncol = 1, rel_heights = c(1, 0.16))
  ggsave(file.path(visualization_output, filename), fig,
         width = 12, height = 14, dpi = 300, units = "in")
  fig
}
recovery_fg <- two_panels(pA, pB + X_TITLE,
                          "combined_true_graph_recovery_findgraphs.pdf")
recovery_sp <- two_panels(pC_rec, pD_rec,
                          "combined_true_graph_recovery_snaq_phynest.pdf")
print(recovery_fg)
print(recovery_sp)
```
