---
title: "PhyNEST Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
library(cowplot)
visual_output <- "../visualization_results/phynest"
phynest_input_dir <- "../phynest_summary"

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("../scripts/visual_utilities.R")
```

## Load and Parse Data
`results/PhyNEST_summary.csv` and `results/PhyNEST_T_threshold.csv` are
written by `scripts/summary_phynest.jl`. Model choice columns without suffix
use the calibrated threshold T* on the per-site statistic
T = (score(h=0) - score(h=1)) / M, where M is the number of sites in the
replicate's alignment (the score difference grows linearly with M, and M is
smaller where fewer loci were retained; column `T_per_site`, the unscaled
difference is column `T`): T* is the 95th percentile of T pooled over the settings without
lineage rate variation (no and gene-specific rates, all duplication/loss
rates), computed separately for each ILS level, as for the WR <= 3.7
threshold of find_graphs. The `_naive` columns use T > 0.
```{r load-parse}
df <- read_csv("../results/PhyNEST_summary.csv") %>%
  mutate(
    dup_loss_rate = as.numeric(
      str_extract(parameter_setting, "(?<=DUP)[0-9.]+")),
    RV = factor(str_extract(parameter_setting, "(?<=RV)[A-Z]+"),
                levels = c("N", "G", "L", "GL")),
    SF = as.numeric(str_extract(parameter_setting, "(?<=SF)[0-9.]+")),
    n_ind = as.integer(str_extract(parameter_setting, "(?<=N_ind)[0-9]+")),
    pct_H0 = `H=0Accepted` / n_reps * 100,
    pct_H1 = `H=1Accepted` / n_reps * 100,
    pct_H_greater = `H>1Accepted` / n_reps * 100,
    pct_H0_naive = `H=0Accepted_naive` / n_reps * 100,
    pct_H1_naive = `H=1Accepted_naive` / n_reps * 100
  ) %>%
  filter(!is.na(RV))

thresholds <- read_csv("../results/PhyNEST_T_threshold.csv")
t_star <- c(low  = thresholds$T_star[thresholds$cell == "SF0.5-N_ind1"],
            high = thresholds$T_star[thresholds$cell == "SF1.0-N_ind1"])
t_star
```

## Model choice: naive rule (T > 0) vs calibrated rule (T > T*)
```{r plot-model-choice}
#| fig-width: 14
#| fig-height: 16
source("../scripts/visual_utilities.R")
p_naive <- plot_hypothesis_acceptance_grid(df,
  h0_col = "pct_H0_naive",
  h1_col = "pct_H1_naive",
  h_greater_col = "pct_H_greater",
  output_dir = visual_output,
  plot_title = "PhyNEST model choice when T > 0",
  output_filename = "PhyNEST_model_choice_naive.png") +
  theme(legend.position = "none", axis.title.x = element_blank())

p_tstar <- plot_hypothesis_acceptance_grid(df,
  value_col_prefix = "pct_",
  h_greater_col = "pct_H_greater",
  output_dir = visual_output,
  plot_title = "PhyNEST model choice when T > T*",
  output_filename = "PhyNEST_model_choice_Tstar.png")

combined <- plot_grid(p_naive, p_tstar, ncol = 1,
                      labels = c("A", "B"), label_size = 18)
png(filename = file.path(visual_output, "PhyNEST_model_choice_combined.png"),
    width = 14, height = 16, units = "in", res = 300)
print(combined)
dev.off()
```

## 95th percentile of T per setting, with T*
Analog of the worst-residual percentile plot for find_graphs: the settings
without lineage rate variation define T*, one per ILS level. Pass
`t_column = "T"` to the plotting functions to see the unscaled T instead.
```{r plot-T-percentiles}
#| fig-width: 8
#| fig-height: 8
p_T <- plot_T_percentiles_jitter(
  input_dir       = phynest_input_dir,
  output_dir      = visual_output,
  output_filename = "PhyNEST_T_95-percentiles_jitter",
  t_star          = t_star,
  facet_label     = "PhyNEST")
print(p_T)
```

## Distribution of T in every setting
```{r plot-T-distributions}
#| fig-width: 12
#| fig-height: 7
p_Tdist <- plot_T_distributions(
  input_dir       = phynest_input_dir,
  output_dir      = visual_output,
  output_filename = "PhyNEST_T_distributions",
  t_star          = t_star)
print(p_Tdist)
```

## Why T is bimodal: where the reticulation is placed
In the settings without lineage rate variation, T has two modes. The upper
mode is the replicates whose h=1 network puts the reticulation between the
(G,H) clade and the rest of the ingroup (hybrid clade B,C,D,E,F with donors
G and/or H); every other placement gives a much smaller gain.
```{r plot-T-by-hybrid-placement}
#| fig-width: 17
#| fig-height: 8
p_placement <- plot_T_by_hybrid_placement(
  input_dir       = phynest_input_dir,
  output_dir      = visual_output,
  output_filename = "PhyNEST_T_by_hybrid_placement",
  t_star          = t_star,
  ratevar         = c("RVN", "RVG"))
print(p_placement)
```

## True tree recovery (h=0 exact, h=1 displayed, h=1 with F pruned)
```{r plot-true-tree-recovery}
#| fig-width: 16
#| fig-height: 8
p_recovery <- plot_true_graph_recovery_lines_aggregated(df,
  output_dir      = visual_output,
  output_filename = "PhyNEST_true_graph_recovery_lines_aggregated.png",
  y_range         = c(0, 102),
  plot_title      = NULL)
print(p_recovery)
```

## Estimated gene flow proportion (minor gamma)
Produced by `summary_phynest.jl`; regenerated here for convenience.
```{r plot-minor-gamma}
#| fig-width: 14
#| fig-height: 8
plot_overlapping_ratevar_by_n_inds_sf(phynest_input_dir,
  "gamma_1", "gamma_2", visual_output, "PhyNEST_minorG", 70)
plot_snaq_minor_gamma_by_tree_display(phynest_input_dir,
  visual_output, "PhyNEST_minor_gamma_by_tree_display",
  method_label = "PhyNEST", split_by_placement = TRUE)
```
