---
title: "Combined Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) 
visualization_output <- "../visualization_results/combined" 
snaq_input_dir <- "../snaq_summary"
findgraph_input_dir <- "../findgraph_summary"
source("../scripts/visual_utilities.R")

# Load summary data frames for functions that take pre-loaded data
parse_params <- function(df, param_col) {
  df %>% mutate(
    dup_loss_rate = as.numeric(str_extract(.data[[param_col]], "(?<=DUP)[0-9]*\\.?[0-9]+(?:[eE][-+]?[0-9]+)?")),
    RV    = factor(str_extract(.data[[param_col]], "(?<=RV)[A-Z]+"), levels = c("N", "G", "L")),
    SF    = as.numeric(str_extract(.data[[param_col]], "(?<=SF)[0-9]*\\.?[0-9]+")),
    N_ind = as.integer(str_extract(.data[[param_col]], "(?<=N_ind)[0-9]+")),
    n_ind = N_ind
  )
}

snaq_df      <- read_csv("../results/SNaQ_summary.csv")      %>% parse_params("parameter_setting")
findgraph_df <- read_csv("../results/findgraph_summary.csv") %>%
  parse_params("paramname_root") %>%
  mutate(
    pct_H0        = H0Accepted / total_replicates * 100,
    pct_H0_wr_3.7 = H0Accepted_WR_3.7 / total_replicates * 100
  )
```

# Combined Plot of minor Gamma SNaQ vs findgraph
Minor gamma values aggregated across all parameter settings (n_inds, ILS, duplication/loss rates)
with substitution rate variation color coding (gene, lineage, none).

```{r combined_snaq_findgraph_minor_gamma, fig.width=14, fig.height=6}

# Create combined 2-panel plot
p_minor_gamma <- plot_combined_snaq_findgraph_aggregated(
  snaq_input_dir = snaq_input_dir,
  findgraph_input_dir = findgraph_input_dir,
  output_dir = visualization_output,
  output_filename = "combined_snaq_findgraph_aggregated",
  max_y = 500
)
print(p_minor_gamma)
```

# Combined Plot of minor Gamma SNaQ vs findgraph for each parameter setting (n_inds, ILS, duplication/loss rates)
Minor gamma values faceted by parameter settings (n_inds, ILS, duplication/loss rates)
with substitution rate variation color coding (gene, lineage, none).

```{r combined_snaq_findgraph_minor_gamma_by_tree_display, fig.width=14, fig.height=18}
source("../scripts/visual_utilities.R")
# Create combined 2-panel plot by tree display visualization
result <- plot_combined_snaq_findgraph_by_tree_display(
  snaq_input_dir = snaq_input_dir,
  findgraph_input_dir = findgraph_input_dir,
  output_dir = visualization_output,
  output_filename = "combined_snaq_findgraph_by_tree_display",
  max_y = 350,
  max_y_by_ratevar = list(none = 250, gene = 350, lineage = 100)
)
print(result)
```


# Combined H=1 True Graph Recovery: SNaQ vs findgraphs

```{r combined_h1_recovery, fig.width=16, fig.height=9}
# SNaQ uses find_true_net1 (% replicates where H=1 finds true graph, across all graphs)
# findgraphs uses pct_true_tree_H1 (same metric)
p_h1_recovery <- plot_combined_true_graph_recovery_H1_only(
  snaq_df      = snaq_df,
  findgraph_df = findgraph_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "pct_true_tree_H1", # among all trees recovered by findgraphs 
  output_dir       = visualization_output,
  output_filename  = "combined_snaq_findgraph_h1_alltrees_for_findgraphs_recovery",
  y_range          = c(75, 105),
  plot_title       = "H=1 True Graph Recovery: SNaQ vs findgraphs"
)
print(p_h1_recovery)
```

```{r combined_h1_best_graph_recovery, fig.width=16, fig.height=9}
# Best-graph version: findgraphs uses count_H1_best_displays_true_tree
source("../scripts/visual_utilities.R") 
p_h1_best <- plot_combined_true_graph_recovery_H1_only(
  snaq_df      = snaq_df,
  findgraph_df = findgraph_df,
  h1_col_snaq      = "find_true_net1",
  h1_col_findgraph = "count_H1_best_displays_true_tree",
  output_dir       = visualization_output,
  output_filename  = "combined_snaq_findgraph_h1_best_graph_recovery",
  y_range          = c(60, 102),
  plot_title       = NULL
)
print(p_h1_best)
```

# Combined Type I Error Rate (H≥1 Accepted): SNaQ vs findgraphs
```{r combined_h0_acceptance, fig.width=16, fig.height=9}
source("../scripts/visual_utilities.R")
p_h0_combined <- plot_combined_hypothesis_acceptance_H0(
  snaq_df               = snaq_df,
  findgraph_df          = findgraph_df,
  h0_col_snaq           = "pct_H0",
  h0_col_findgraph_wr30 = "pct_H0",
  h0_col_findgraph_wr37 = "pct_H0_wr_3.7",
  output_dir            = visualization_output,
  output_filename       = "combined_snaq_findgraph_type1_error",
  y_range               = c(-5, 105),
  plot_title            = NULL
)
print(p_h0_combined)
```

