
---
title: "Simulation Results Visualization"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)
library(patchwork)
library(cowplot)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) 
```

## Load and Parse Data
```{r load-csv}
df <- read_csv("../results/summary_concatenated.csv") 
outdir <- "../visualization_results/simulation"
if (!dir.exists(outdir)) {
  dir.create(outdir, recursive = TRUE)
} 
```
```{r parse-data}
# Parse parameter_setting column
df <- df %>%
  mutate(
    dup_loss_rate = as.numeric(str_extract(parameter_setting,
      "(?<=DUP)[0-9.e+-]+(?=-)")),
    RV = str_extract(parameter_setting, "(?<=RV)[A-Z]+"),
    N_inds = as.integer(str_extract(parameter_setting, "(?<=N_ind)[0-9]+")),
    SF = as.numeric(str_extract(parameter_setting, "(?<=SF)[0-9.]+(?=(-|$))")),
    genelen = as.integer(str_extract(parameter_setting, "(?<=genelen)[0-9]+"))
  )

# Display parsed columns and check unique values
df %>% 
  select(parameter_setting, dup_loss_rate, RV, N_inds, SF, genelen) %>%
  head(10)

# Check unique values for each parameter
cat("Unique dup_loss_rate:", unique(df$dup_loss_rate), "\n")
cat("Unique SF:", unique(df$SF), "\n")
cat("Unique RV:", unique(df$RV), "\n")
cat("Unique N_inds:", unique(df$N_inds), "\n")
```

## Gene Events and Hidden Paralogy
```{r plot_events}
# Prepare data for plotting
plot_data <- df %>%
  select(dup_loss_rate, SF, RV, N_inds,
         pert_false_HP, pert_weak_HP, pert_strong_HP) %>%
  pivot_longer(cols = starts_with("pert_"), 
               names_to = "metric", 
               values_to = "percentage") %>%
  mutate(
    dup_loss_rate = factor(dup_loss_rate),
    SF = factor(SF),
    RV = factor(RV),
    N_inds = factor(N_inds),
    metric = factor(metric, levels = c(
      "pert_false_HP", "pert_weak_HP", "pert_strong_HP"
    )),
    metric_label = recode(metric,
      "pert_false_HP" = "false HP",
      "pert_weak_HP" = "weak HP",
      "pert_strong_HP" = "strong HP"
    ),
    # Create ILS label
    ILS_label = recode(SF,
      "0.5" = "low ILS",
      "1" = "high ILS"
    ),
    # Create individual per taxon label
    N_inds_label = paste(N_inds, "individual per taxon"),
    # Create combined shape factor (4 levels: 2 N_inds × 2 SF)
    shape_group = interaction(N_inds_label, ILS_label, sep = ", "),
    # Recode RV labels with specific order for color assignment
    RV_label = factor(recode(RV,
      "G" = "gene",
      "L" = "lineage",
      "N" = "none"
    ), levels = c("gene", "lineage", "none"))
  )

# Create combined plot with facet_grid
p_combined <- ggplot(plot_data, aes(x = dup_loss_rate, y = percentage, 
                                     color = RV_label, shape = shape_group)) +
  geom_point(size = 4, alpha = 0.7,
             position = position_jitter(width = 0.2, height = 0)) +
  facet_grid(~ metric_label, scales = "fixed") +
  scale_color_manual(values = c("gene" = "#039afe", 
                                 "lineage" = "#fbc531", 
                                 "none" = "#898686")) +
  labs(title = "hidden paralogy across simulation conditions",
       x = "dup/loss rate",
       y = "percentage",
       color = "substitution rate variation",
       shape = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.box = "vertical")

ggsave(file.path(outdir, "percentage_events_plot_combined.pdf"),
       plot = p_combined, width = 10, height = 5, units = "in")
print(p_combined)

```

## Summary Statistics: Hidden Paralogy by Duplication/Loss Rate
It seems SF and RateVar do not change HP statistics, so we summarize
HP stats by N_inds and dup_loss_rate.
```{r summary-hp}
summary_df <- df %>%
  group_by(dup_loss_rate) %>%
  summarise(
    n_genes_mean = round(mean(n_genes_mean, na.rm = TRUE),1),
    n_genes_min = round(mean(n_genes_mean, na.rm = TRUE),1),
    n_iterations = round(mean(n_iterations, na.rm = TRUE),1), 
    False_HP_mean = round(mean(pert_false_HP, na.rm = TRUE),1),
    False_HP_sd = round(sd(pert_false_HP, na.rm = TRUE),2),
    Weak_HP_mean = round(mean(pert_weak_HP, na.rm = TRUE),1),
    Weak_HP_sd = round(sd(pert_weak_HP, na.rm = TRUE),2),
    Strong_HP_mean = round(mean(pert_strong_HP, na.rm = TRUE),1),
    Strong_HP_sd = round(sd(pert_strong_HP, na.rm = TRUE),2),
    pert_gene_tree_noDupLoss_mean = round(
      mean(pert_trees_experiencing_nothing, na.rm = TRUE), 1),
    pert_gene_tree_noDupLoss_sd = round(
      sd(pert_trees_experiencing_nothing, na.rm = TRUE), 2),
    .groups = "drop", 
  ) %>%
  arrange(dup_loss_rate)
print(summary_df, width = Inf)
```


### RF metric graphs 

```{r prepare-rf-data}
# ── Sort rows by dup_loss_rate > RV > SF > N_inds ────────────────────────────
df_heat <- df %>%
  arrange(dup_loss_rate, RV, SF, N_inds) %>%
  mutate(
    RV_label   = factor(recode(RV, "G" = "gene", "L" = "lineage", "N" = "none"),
                        levels = c("none", "gene", "lineage")),
    SF_label   = factor(
      ifelse(SF == 0.5, "low ILS (SF=0.5)", "high ILS (SF=1.0)"),
      levels = c("low ILS (SF=0.5)", "high ILS (SF=1.0)")),
    dup_label  = factor(paste0("DUP=", dup_loss_rate),
                        levels = paste0("DUP=", sort(unique(dup_loss_rate)))),
    N_label    = factor(paste0(N_inds, " ind/taxon"),
                        levels = c("1 ind/taxon", "2 ind/taxon")),
    row_id     = paste0(dup_loss_rate, "|", RV, "|", SF, "|", N_inds),
    row_id     = factor(row_id, levels = rev(unique(row_id))) # DUP0 first
  )
```

Point plots for two metric groups: gene tree discordance (true gene tree
vs species tree) and gene tree estimation error (true vs estimated).
Each point is one parameter combination, colored by RV, shaped by
SF/N_inds. Faceted by HP category. NoF metrics excluded.

```{r rf-point-plots, fig.width=14, fig.height=16}
# ── 1. Prepare data for point plots ──────────────────────────────────────────
# Select four HP category columns per group (exclude _all, noF columns)
df_point_plot <- df_heat %>%
  select(
    dup_loss_rate, RV_label, SF_label, N_label,
    mean_RF_genetree_vs_sptree_nothing,
    mean_RF_genetree_vs_sptree_false_HP,
    mean_RF_genetree_vs_sptree_weak_HP,
    mean_RF_genetree_vs_sptree_strong_HP,
    mean_RF_true_vs_est_genetree_nothing,
    mean_RF_true_vs_est_genetree_false_HP,
    mean_RF_true_vs_est_genetree_weak_HP,
    mean_RF_true_vs_est_genetree_strong_HP
  )

# Pivot to long format
df_point_long <- df_point_plot %>%
  pivot_longer(
    cols = starts_with("mean_RF_"),
    names_to = "metric",
    values_to = "RF"
  ) %>%
  mutate(
    # Extract HP category from metric name
    hp_category = case_when(
      str_detect(metric, "_nothing$") ~ "no dup/loss",
      str_detect(metric, "_false_HP$") ~ "false HP",
      str_detect(metric, "_weak_HP$") ~ "weak HP",
      str_detect(metric, "_strong_HP$") ~ "strong HP",
      TRUE ~ "other"
    ),
    hp_category = factor(hp_category,
      levels = c("no dup/loss", "false HP", "weak HP", "strong HP")),
    
    # Identify metric group for faceting
    metric_group = ifelse(str_detect(metric, "genetree_vs_sptree"), 
                          "gene tree discordance", 
                          "Gene tree estimation error"),
    
    # Create shape and fill aesthetics based on visual_utilities.R
    combo = case_when(
      SF_label == "high ILS (SF=1.0)" & N_label == "1 ind/taxon" ~
        "ILS = high, n = 1",
      SF_label == "high ILS (SF=1.0)" & N_label == "2 ind/taxon" ~
        "ILS = high, n = 2",
      SF_label == "low ILS (SF=0.5)" & N_label == "1 ind/taxon" ~
        "ILS = low, n = 1",
      SF_label == "low ILS (SF=0.5)" & N_label == "2 ind/taxon" ~
        "ILS = low, n = 2"
    ),
    combo = factor(combo, levels = c(
      "ILS = high, n = 1", "ILS = high, n = 2",
      "ILS = low, n = 1", "ILS = low, n = 2")),
    fill_color = ifelse(
      N_label == "1 ind/taxon", as.character(RV_label), "hollow"),
    # Format x-axis labels: 0 → "no dup/loss", others → scientific notation
    dup_loss_label = ifelse(
      dup_loss_rate == 0, "no dup/loss",
      sub("e-0", "e-", formatC(dup_loss_rate, format = "e", digits = 0))
    )
  ) %>%
  # Remove dup_loss_rate = 0 for HP panels (no duplication events possible)
  filter(!(hp_category %in% c("false HP", "weak HP", "strong HP") &
           dup_loss_rate == 0)) %>%
  mutate(
    dup_loss_label = factor(dup_loss_label,
      levels = c("no dup/loss",
        sub("e-0", "e-",
          formatC(sort(unique(dup_loss_rate[dup_loss_rate > 0])),
                  format = "e", digits = 0))))
  )

# ── 2. Define colors and shapes ──────────────────────────────────────────────
rv_colors_point <- c("none" = "#898686", "gene" = "#039afe",
                     "lineage" = "#fbc531")
fill_values <- c(rv_colors_point, "hollow" = "white")
shape_values <- setNames(
  c(21, 21, 24, 24),
  c("ILS = high, n = 1", "ILS = high, n = 2",
    "ILS = low, n = 1", "ILS = low, n = 2"))



# ── 3. Create the "gene tree discordance" plot ───────────────────────────────
plot_data_discordance <- df_point_long %>%
  filter(metric_group == "gene tree discordance")

p_discordance <- ggplot(plot_data_discordance,
                        aes(x = dup_loss_label, y = RF,
                            color = RV_label, shape = combo,
                            fill = fill_color)) +
  geom_point(position = position_jitter(width = 0.2, height = 0),
             size = 4, stroke = 1) +
  facet_wrap(~ hp_category, scales = "free_x", nrow = 1) +
  scale_color_manual(values = rv_colors_point,
                     name = "rate variation:",
                     labels = c("none" = "none",
                                "gene" = "across genes",
                                "lineage" = "across lineages")) +
  scale_fill_manual(values = fill_values, guide = "none") +
  scale_shape_manual(values = shape_values,
                     name = "ILS & individuals / taxon (n):    ") +
  scale_y_continuous(limits = c(0.20, 0.40)) +
  labs(
    x = NULL,
    y = "true gene vs species trees"
  ) +
  theme_bw(base_size = 18) +
  theme(
    legend.position   = "bottom",
    axis.title        = element_text(size = 20, face = "bold"),
    axis.text.x       = element_text(
      angle = 45, hjust = 1, size = 16, face = "bold", color = "black"),
    axis.text.y       = element_text(size = 16, face = "bold", color = "black"),
    strip.text        = element_text(size = 20, face = "bold"),
    strip.background  = element_rect(fill = "grey90"),
    legend.text       = element_text(size = 16, face = "bold"),
    legend.title      = element_text(size = 16, face = "bold")
  ) +
  guides(
    color = guide_legend(override.aes = list(size = 5, stroke = 1.2), nrow = 1),
    shape = guide_legend(override.aes = list(
      size   = 5, stroke = 1.2,
      fill   = c("grey55", "white", "grey55", "white")
    ), nrow = 1)
  )

# ── 4. Create the "Gene tree estimation error" plot ──────────────────────────
plot_data_estimation <- df_point_long %>%
  filter(metric_group == "Gene tree estimation error")

p_estimation <- ggplot(plot_data_estimation,
                       aes(x = dup_loss_label, y = RF,
                           color = RV_label, shape = combo,
                           fill = fill_color)) +
  geom_point(position = position_jitter(width = 0.2, height = 0),
             size = 4, stroke = 1) +
  facet_wrap(~ hp_category, scales = "free_x", nrow = 1) +
  scale_color_manual(values = rv_colors_point,
                     name = "rate variation:",
                     labels = c("none" = "none",
                                "gene" = "across genes",
                                "lineage" = "across lineages")) +
  scale_fill_manual(values = fill_values, guide = "none") +
  scale_shape_manual(values = shape_values,
                     name = "ILS & individuals / taxon (n):    ") +
  scale_y_continuous(limits = c(0.05, 0.25)) +
  labs(
    x = NULL,
    y = "true vs estimated gene trees"
  ) +
  theme_bw(base_size = 18) +
  theme(
    legend.position   = "bottom",
    axis.title        = element_text(size = 20, face = "bold"),
    axis.text.x       = element_text(
      angle = 45, hjust = 1, size = 16, face = "bold", color = "black"),
    axis.text.y       = element_text(size = 16, face = "bold", color = "black"),
    strip.text        = element_text(size = 20, face = "bold"),
    strip.background  = element_rect(fill = "grey90"),
    legend.text       = element_text(size = 16, face = "bold"),
    legend.title      = element_text(size = 16, face = "bold")
  ) +
  guides(
    color = guide_legend(override.aes = list(size = 5, stroke = 1.2), nrow = 1),
    shape = guide_legend(override.aes = list(
      size   = 5, stroke = 1.2,
      fill   = c("grey55", "white", "grey55", "white")
    ), nrow = 1)
  )

# ── 5. Assemble combined figure with cowplot ──────────────────────────────────

# Build a shared legend source: each guide gets its own boxed background via
# guide_legend(theme = ...), mirroring the style in visual_combined.qmd.
p_for_shared_legend <- p_discordance +
  guides(
    color = guide_legend(
      name           = "rate variation:",
      title.position = "top",
      override.aes   = list(size = 5, stroke = 1.2),
      nrow           = 3,
      theme          = theme(
        legend.background = element_rect(
          color = "black", linewidth = 1.2, fill = "white"),
        legend.margin     = margin(6, 10, 6, 10),
        legend.text       = element_text(size = 13, face = "bold"),
        legend.title      = element_text(size = 13, face = "bold")
      )
    ),
    shape = guide_legend(
      name           = "ILS & individuals / taxon (n):",
      title.position = "top",
      override.aes   = list(size  = 5, stroke = 1.2,
                            fill  = c("grey55", "white", "grey55", "white"),
                            color = "black"),
      nrow           = 2,
      theme          = theme(
        legend.background = element_rect(
          color = "black", linewidth = 1.2, fill = "white"),
        legend.margin     = margin(6, 10, 6, 10),
        legend.text       = element_text(size = 13, face = "bold"),
        legend.title      = element_text(size = 13, face = "bold")
      )
    ),
    fill = "none"
  ) +
  theme(
    legend.position  = "bottom",
    legend.box       = "horizontal",
    legend.spacing.x = unit(1.0, "lines")
  )

# Single combined legend: rate variation (left box), ILS × N (right box)
legend_row <- cowplot::get_legend(p_for_shared_legend)

# Row 1 (top): discordance — suppress x-axis tick labels and ticks, no legend
p_disc_clean <- p_discordance +
  theme(
    legend.position = "none",
    axis.text.x     = element_blank(),
    axis.ticks.x    = element_blank()
  )

# Row 2 (bottom): estimation error — keep x-axis tick labels, no legend
p_est_clean <- p_estimation +
  theme(legend.position = "none")

# Row-label helper
make_row_label <- function(label) {
  ggplot(data.frame(x = 1, y = 1), aes(x = x, y = y)) +
    labs(y = label) +
    theme_void() +
    theme(
      axis.title.y = element_text(size = 18, face = "bold", angle = 90,
                                   vjust = 0.5, hjust = 0.5)
    )
}

label_disc <- make_row_label("gene tree discordance:")
label_est  <- make_row_label("gene tree estimation error:")

# Assemble each row: narrow label column + main plot
row1 <- plot_grid(label_disc, p_disc_clean, nrow = 1, rel_widths = c(0.04, 1))
row2 <- plot_grid(label_est,  p_est_clean,  nrow = 1, rel_widths = c(0.04, 1))

# Stack rows then append shared boxed legends at the bottom
p_combined_rf <- plot_grid(
  row1, row2, legend_row,
  ncol = 1,
  rel_heights = c(0.8, 1, 0.25),
  labels = c("A", "B", ""),
  label_size = 20,
  label_fontface = "bold"
)

print(p_combined_rf)

pdf(file.path(outdir, "rf_point_plot_combined.pdf"), width = 10, height = 12)
print(p_combined_rf)
dev.off()
```

## RF Summary Table

```{r rf-summary-table}
library(knitr)

# helper: compute mean/sd/median/n for a given grouping
# n counts distinct parameter settings (not rows), since df_point_long has
# multiple rows per setting (one per HP category after pivoting).
summarise_RF <- function(data, ...) {
  data %>%
    group_by(...) %>%
    summarise(
      mean   = round(mean(RF,   na.rm = TRUE), 4),
      sd     = round(sd(RF,     na.rm = TRUE), 4),
      median = round(median(RF, na.rm = TRUE), 4),
      n      = n_distinct(interaction(
                 dup_loss_rate, RV_label, SF_label, N_label,
                 drop = TRUE)),
      .groups = "drop"
    )
}

# ── By rate variation ─────────────────────────────────────────────────────────
tbl_rv <- summarise_RF(df_point_long,
  `metric group`  = metric_group,
  `rate variation` = RV_label
) %>% arrange(`metric group`, `rate variation`)

# ── By ILS level ──────────────────────────────────────────────────────────────
tbl_ils <- summarise_RF(df_point_long,
  `metric group` = metric_group,
  `ILS`          = SF_label
) %>% arrange(`metric group`, `ILS`)

# ── By HP category ────────────────────────────────────────────────────────────
tbl_hp <- summarise_RF(df_point_long,
  `metric group` = metric_group,
  `HP category`  = hp_category
) %>% arrange(`metric group`, `HP category`)

# ── By dup/loss rate ──────────────────────────────────────────────────────────
tbl_dup <- summarise_RF(df_point_long,
  `metric group`  = metric_group,
  `dup/loss rate` = dup_loss_label
) %>% arrange(`metric group`, `dup/loss rate`)

# ── By n ind/taxon ────────────────────────────────────────────────────────────
tbl_n <- summarise_RF(df_point_long,
  `metric group` = metric_group,
  `n ind/taxon`  = N_label
) %>% arrange(`metric group`, `n ind/taxon`)

# ── By ILS x HP category ──────────────────────────────────────────────────────
tbl_ils_hp <- summarise_RF(df_point_long,
  `metric group` = metric_group,
  `ILS`          = SF_label,
  `HP category`  = hp_category
) %>% arrange(`metric group`, `ILS`, `HP category`)

# ── By ILS x strong HP vs non-strong HP ───────────────────────────────────────
tbl_ils_strongHP <- df_point_long %>%
  mutate(
    hp_group = ifelse(
      hp_category == "strong HP", "strong HP", "non-strong HP"),
    hp_group = factor(hp_group,
                      levels = c("non-strong HP", "strong HP"))) %>%
  summarise_RF(`metric group` = metric_group,
               `ILS`          = SF_label,
               `HP group`     = hp_group) %>%
  arrange(`metric group`, `ILS`, `HP group`)

# ── Print each table ──────────────────────────────────────────────────────────
kable(tbl_rv,  caption = "RF by rate variation (across all other factors)")
kable(tbl_ils, caption = "RF by ILS level (across all other factors)")
kable(tbl_hp,  caption = "RF by HP category (across all other factors)")
kable(tbl_dup, caption = "RF by dup/loss rate (across all other factors)")
kable(tbl_n,   caption = "RF by n ind/taxon (across all other factors)")
kable(tbl_ils_hp,       caption = "RF by ILS x HP category")
kable(tbl_ils_strongHP, caption = "RF by ILS x strong HP vs non-strong HP")

# ── Save all to one CSV with a 'grouping factor' column ───────────────────────
sel_cols <- c("`metric group`", "category", "level",
              "mean", "sd", "median", "n")
rf_summary_all <- bind_rows(
  tbl_rv %>% mutate(category = "rate variation",
    level = as.character(`rate variation`)) %>%
    select(`metric group`, category, level, mean, sd, median, n),
  tbl_ils %>% mutate(category = "ILS",
    level = as.character(`ILS`)) %>%
    select(`metric group`, category, level, mean, sd, median, n),
  tbl_hp %>% mutate(category = "HP category",
    level = as.character(`HP category`)) %>%
    select(`metric group`, category, level, mean, sd, median, n),
  tbl_dup %>% mutate(category = "dup/loss rate",
    level = as.character(`dup/loss rate`)) %>%
    select(`metric group`, category, level, mean, sd, median, n),
  tbl_n %>% mutate(category = "n ind/taxon",
    level = as.character(`n ind/taxon`)) %>%
    select(`metric group`, category, level, mean, sd, median, n),
  tbl_ils_hp %>% mutate(category = "ILS x HP category",
    level = paste0(as.character(`ILS`), " | ",
                   as.character(`HP category`))) %>%
    select(`metric group`, category, level, mean, sd, median, n),
  tbl_ils_strongHP %>% mutate(category = "ILS x strong HP",
    level = paste0(as.character(`ILS`), " | ",
                   as.character(`HP group`))) %>%
    select(`metric group`, category, level, mean, sd, median, n)
)

write.csv(rf_summary_all,
          file.path(outdir, "rf_summary_table.csv"), row.names = FALSE)
```


